### 2024-06-11 manuscript.Rmd
added image some formatting knitr images

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

@@

![](img/rstudio-screenshot-marker2.png)
In this example, the R Markdown document is knitted into a HTML-report.
On document generation, the R code in the `reproducibleR`-chunk is executed and the value of `my_sum` is stored in a separate file. 
A reproducibility report is shown below the code chunk to indicate all variables of the given chunk whose data are stored. The following is a snippet from the HTML generated on the first ever creation of the document:

![](img/generation-step1.png)
Once the document is generated a second time and the reproducibility data exists, the computation is executed anew and its results are compared to the stored reproducibility information on a variable by variable basis.
The reproducibility report will now contain information about the success of the individual reproduction attempts.
In our example, the computation was reproduced successfully:

![](img/generation-step2.png)
If the document is regenerated and the computational result is not identical to the original result, this failure of reproduction is indicated in the reproducibility report.
In this example, if someone changed the value of `x`, variable `my_sum` would change and the following failure would be displayed:

![](img/generation-step2-failed.png)

@@

```{r echo=FALSE, eval=TRUE, results="asis"}
jsonlite::serializeJSON(numbers_ex)
```

@@

```{r echo=FALSE, eval=TRUE, results="asis"}
jsonlite::serializeJSON(digest::digest(numbers_ex,algo = "sha256"))
```

In addition to the contents of all newly declared variables in a `reproducibleR`-chunk, the package also stores fingerprints of the code syntax.
This is shown in the following schematic figure:
![](img/schema-json-fingerprints.png)

>>>>

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

@@

```{r rstudio-screen1, fig.cap=""}
knitr::include_graphics("img/rstudio-screenshot-marker2.png")
```

In this example, the R Markdown document is knitted into a HTML-report.
On document generation, the R code in the `reproducibleR`-chunk is executed and the value of `my_sum` is stored in a separate file. 
A reproducibility report is shown below the code chunk to indicate all variables of the given chunk whose data are stored. The following is a snippet from the HTML generated on the first ever creation of the document:

```{r rstudio-screen2, fig.cap="Snippet from a knitted Markdown file showing the reproducibility report when a document is generated for the first time."}
knitr::include_graphics("img/generation-step1.png")
```
Once the document is generated a second time and the reproducibility data exists, the computation is executed anew and its results are compared to the stored reproducibility information on a variable by variable basis.
The reproducibility report will now contain information about the success of the individual reproduction attempts.
In our example, the computation was reproduced successfully:

```{r rstudio-screen3, fig.cap="Snippet from a knitted Markdown file showing the reproducibility report when a document is re-generated and a variable is successfully reproduced."}
knitr::include_graphics("img/generation-step2.png")

```
If the document is regenerated and the computational result is not identical to the original result, this failure of reproduction is indicated in the reproducibility report.
In this example, if someone changed the value of `x`, variable `my_sum` would change and the following failure would be displayed:

```{r rstudio-screen4, fig.cap="Snippet from a knitted Markdown file showing the reproducibility report when a document is re-generated and the reproduction of a variable failed."}
knitr::include_graphics("img/generation-step2-failed.png")

```

@@

```{r echo=FALSE, eval=TRUE, results="asis"}
jsonlite::serializeJSON(numbers_ex, pretty=TRUE)
```

@@

```{r echo=FALSE, eval=TRUE, results="asis"}
jsonlite::serializeJSON(digest::digest(numbers_ex,algo = "sha256"),pretty=TRUE)
```

In addition to the contents of all newly declared variables in a `reproducibleR`-chunk, the package also stores fingerprints of the code syntax.
This is shown in the schematic in Figure \@ref(ref:jsonschema).
```{r jsonschema, fig.cap="(ref:jsonschema)A JSON file stores fingerprints of all newly declared variables in a reproducibleR-chunk as well as fingerprints of the code chunk syntax."}
knitr::include_graphics("img/schema-json-fingerprints.png")

```
